Exploatarea Software și Mai Departe: Dezvăluirea Vectorilor de Atac și Contra-Măsurilor în Calculul Modern / Software Exploitation and Beyond: Unveiling Attack Vectors and Countermeasures in Modern Computing

### 2023-06-23 paper.tex
Pepe

Now that we have the first issue fixed, how do we pass parameters to the functions
we want to call? Because the NX (No-Execute) bit

@@

\subsection{Browser exploits}

\begin{comment}
Cool decision tree
\end{comment}

\subsection{State of the art}
\begin{comment}
  Rise of the hypervizor exploits (showcase some virtualbox exploits, maybe
  vmware hyperv) RCE Exploits mostly slowing down Common techniques no longer
  being effective (check offbyonesec talk about windows kernel exploitation, talk
  about)
\end{comment}

>>>>

Now that we have the first issue fixed, how do we pass parameters to the functions
we want to call? Because the NX (No-Execute) bit is enabled and all executable
regions of code are read-only in order to prevent shellcode, we are going to chain
together multiple addresses that point to small code chunks ending in the
\emph{ret} instruction

@@

\subsection{Browser exploits}
In the contemporary computing landscape, a notable surge in interest surrounding
browser exploitation has emerged, predominantly attributed to the increasing
ubiquity of JavaScript and the inherent security implications of executing
foreign code on local machines. As web applications have become more complex and
feature-rich, JavaScript's role has evolved from simple client-side scripting to
powering extensive, intricate software systems. This growth presents an enticing
target for threat actors, as virtually every user who interacts with a web
application is running potentially untrusted code within their local execution
context. The browser environment thus turns into a frontline for cybersecurity,
demanding rigorous scrutiny and sophisticated mitigation techniques.
Furthermore, the heterogeneous nature of browser architecture and JavaScript
engine implementations across different vendors adds a layer of complexity to
securing these environments. This highlights the criticality of understanding
and countering browser-based exploits, forming an essential dimension of
comprehensive cybersecurity strategies.

\subsubsection{How does JavaScript get exploited?}
Within the context of JavaScript, a dynamic and interpreted language primarily
executed within the confines of web browsers, a unique vulnerability surface
emerges, closely tied to its heap-based memory management and dynamic typing
semantics. The vast majority of JavaScript objects are allocated on the heap,
the malleability of which introduces inherent susceptibilities to heap overflow
attacks. The manipulation of an object's memory layout, made possible through an
overflow, can fundamentally alter an object's behaviour, given JavaScript's
dynamic typing system.

This means that a successfully exploited heap overflow
could potentially morph an innocuous object into a malicious entity with
escalated privileges or unintended functionalities. As such, heap overflow
vulnerabilities within JavaScript engines pose a significant security concern,
mandating careful consideration and robust mitigation strategies in the design
and implementation of modern JavaScript engines and runtime environments.

We will continue by looking at the structure of how Javascript values (or
JSValues) are encoded into memory:

    % Define matrix
    \matrix [matrix of nodes,
    nodes=block,
    column sep=0cm,
    row sep=0cm
    ] (stack) {
      {\verb|0000:PPPP:PPPP:PPPP|\footnotemark} \\
      {\verb|0001:DDDD:DDDD:DDDD|\footnotemark} \\
      {...} \\
      {\verb|FFFE:DDDD:DDDD:DDDD|} \\
      {\verb|FFFF:0000:IIII:IIII|\footnotemark} \\
    };

\footnotetext{Pulel}
\footnotetext{Pulel}
\footnotetext{Pulel}
This behaviour also extends to more complex and interesting objects such as
arrays. JavaScriptCore (at least the versions from around 2016) describe arrays
as ``exotic'' objects which contain their properties. An in detail explanation
of how these objects are laid out in memory and how to exploit them in\cite{paper
frakck}

Due to the high impact that a vulnerability in a JavaScript runtime would have
on the security of computers all over the world, properly isolating the JS runtime
from the host machine is paramount. In modern browsers this is achieved by
employing the least privilege principle. The browser itself is separated into
multiple processes that use a well defined IPC mechanism to communicate, limiting
what attackers can do by exploiting a single process and requiring an exploit
chain to gain increasingly more privileges as desired.

\subsection{State of the art}
\begin{comment}
  Rise of the hypervizor exploits (showcase some virtualbox exploits, maybe
  vmware hyperv) RCE Exploits mostly slowing down Common techniques no longer
  being effective (check offbyonesec talk about windows kernel exploitation, talk
  about)
\end{comment}
In recent years, virtualization technologies have witnessed an unprecedented
surge in their adoption, largely driven by advancements in datacenter and
cloud-based applications. These technologies allow multiple virtual machines or
containers, each encapsulating an entire execution environment, to coexist on
the same physical hardware, thereby promoting efficient resource utilization,
simplified management, and scalability. More than just a cost-effective solution
for large-scale computations, virtualization has also garnered considerable
attention as a robust approach for isolating the execution of untrusted code. In
this context, it serves as a defensive boundary, segregating potentially harmful
operations within a contained environment, thereby limiting their ability to
adversely affect the larger system. Consequently, the evolution of
virtualization technologies has profoundly impacted the modern computing
landscape, opening new possibilities for efficient, scalable, and secure
computing, but also posing new challenges for cybersecurity.
